\begin{Schunk}
\begin{Sinput}
 library(rockchalk)
 mcDiagnose(bush1)
\end{Sinput}
\begin{Soutput}
The following auxiliary models are being estimated and returned in a list:
partyidDem. ~ `partyidInd. Near Dem.` + partyidIndependent + 
    `partyidInd. Near Repub.` + partyidRepub. + `partyidStrong Repub.` + 
    sexFemale + owngunYES
<environment: 0x3eb4560>
`partyidInd. Near Dem.` ~ partyidDem. + partyidIndependent + 
    `partyidInd. Near Repub.` + partyidRepub. + `partyidStrong Repub.` + 
    sexFemale + owngunYES
<environment: 0x3eb4560>
partyidIndependent ~ partyidDem. + `partyidInd. Near Dem.` + 
    `partyidInd. Near Repub.` + partyidRepub. + `partyidStrong Repub.` + 
    sexFemale + owngunYES
<environment: 0x3eb4560>
`partyidInd. Near Repub.` ~ partyidDem. + `partyidInd. Near Dem.` + 
    partyidIndependent + partyidRepub. + `partyidStrong Repub.` + 
    sexFemale + owngunYES
<environment: 0x3eb4560>
partyidRepub. ~ partyidDem. + `partyidInd. Near Dem.` + partyidIndependent + 
    `partyidInd. Near Repub.` + `partyidStrong Repub.` + sexFemale + 
    owngunYES
<environment: 0x3eb4560>
`partyidStrong Repub.` ~ partyidDem. + `partyidInd. Near Dem.` + 
    partyidIndependent + `partyidInd. Near Repub.` + partyidRepub. + 
    sexFemale + owngunYES
<environment: 0x3eb4560>
sexFemale ~ partyidDem. + `partyidInd. Near Dem.` + partyidIndependent + 
    `partyidInd. Near Repub.` + partyidRepub. + `partyidStrong Repub.` + 
    owngunYES
<environment: 0x3eb4560>
owngunYES ~ partyidDem. + `partyidInd. Near Dem.` + partyidIndependent + 
    `partyidInd. Near Repub.` + partyidRepub. + `partyidStrong Repub.` + 
    sexFemale
<environment: 0x3eb4560>
Drum roll please! 

And your R_j Squareds are (auxiliary Rsq)
            partyidDem.   partyidInd. Near Dem. 
                0.39471                 0.31465 
     partyidIndependent partyidInd. Near Repub. 
                0.26782                 0.22589 
          partyidRepub.    partyidStrong Repub. 
                0.40933                 0.38675 
              sexFemale               owngunYES 
                0.02243                 0.03130 
The Corresponding VIF, 1/(1-R_j^2)
            partyidDem.   partyidInd. Near Dem. 
                  1.652                   1.459 
     partyidIndependent partyidInd. Near Repub. 
                  1.366                   1.292 
          partyidRepub.    partyidStrong Repub. 
                  1.693                   1.631 
              sexFemale               owngunYES 
                  1.023                   1.032 
Bivariate Correlations for design matrix 
                        partyidDem.
partyidDem.                    1.00
partyidInd. Near Dem.         -0.17
partyidIndependent            -0.15
partyidInd. Near Repub.       -0.13
partyidRepub.                 -0.23
partyidStrong Repub.          -0.21
sexFemale                      0.07
owngunYES                     -0.06
                        partyidInd. Near Dem.
partyidDem.                             -0.17
partyidInd. Near Dem.                    1.00
partyidIndependent                      -0.11
partyidInd. Near Repub.                 -0.10
partyidRepub.                           -0.18
partyidStrong Repub.                    -0.16
sexFemale                               -0.02
owngunYES                               -0.04
                        partyidIndependent
partyidDem.                          -0.15
partyidInd. Near Dem.                -0.11
partyidIndependent                    1.00
partyidInd. Near Repub.              -0.08
partyidRepub.                        -0.15
partyidStrong Repub.                 -0.14
sexFemale                            -0.03
owngunYES                             0.04
                        partyidInd. Near Repub.
partyidDem.                               -0.13
partyidInd. Near Dem.                     -0.10
partyidIndependent                        -0.08
partyidInd. Near Repub.                    1.00
partyidRepub.                             -0.13
partyidStrong Repub.                      -0.12
sexFemale                                 -0.04
owngunYES                                  0.00
                        partyidRepub.
partyidDem.                     -0.23
partyidInd. Near Dem.           -0.18
partyidIndependent              -0.15
partyidInd. Near Repub.         -0.13
partyidRepub.                    1.00
partyidStrong Repub.            -0.22
sexFemale                       -0.04
owngunYES                        0.04
                        partyidStrong Repub.
partyidDem.                            -0.21
partyidInd. Near Dem.                  -0.16
partyidIndependent                     -0.14
partyidInd. Near Repub.                -0.12
partyidRepub.                          -0.22
partyidStrong Repub.                    1.00
sexFemale                              -0.03
owngunYES                               0.11
                        sexFemale owngunYES
partyidDem.                  0.07     -0.06
partyidInd. Near Dem.       -0.02     -0.04
partyidIndependent          -0.03      0.04
partyidInd. Near Repub.     -0.04      0.00
partyidRepub.               -0.04      0.04
partyidStrong Repub.        -0.03      0.11
sexFemale                    1.00     -0.11
owngunYES                   -0.11      1.00
\end{Soutput}
\end{Schunk}
